\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-01-13 doc/publications/plos16/plos16.tex
put T1 fontenc back in
little change
some more changes

We also frequently see highly-ranked variants in chromosome 22q11

>>>>

We also frequently see highly-ranked variants in chromosome 22q11. Stagi2010 observe that individuals with a microdeletion
in this region have a significant in bone mass.\ref{Stagi2010} In this same region, we also observe variants present within the
PRODH gene---a gene which is overexpressed in bone.
